%% $Id: factsheet.in.tex 31978 2013-04-02 21:09:37Z goodell $

\documentclass[9pt]{article}
\usepackage{fancyhdr}
\usepackage[usenames]{color}
\usepackage{colortbl}

\pdfpagewidth 8.5in
\pdfpageheight 11in

\setlength\topmargin{-0.6in}
\setlength\oddsidemargin{-0.5in}
\setlength\evensidemargin{-0.5in}
\setlength\textheight{9in}
\setlength\textwidth{7.5in}
\setlength{\parindent}{0in}
\renewcommand{\ttdefault}{lmtt}
\renewcommand{\sfdefault}{phv}
\setlength\parskip{0.0\baselineskip}
\newfont{\bigfont}{phvb at 27pt}

\definecolor{phaseGrey}{rgb}{.4414, .4414, .4571}
\definecolor{phaseGold}{rgb}{.8125, .4883, .0177}
\definecolor{lightGrey}{rgb}{.7414, .7414, .7571}

\setlength\extrarowheight{2pt}

\begin{document}

\linespread{0.85}
\headheight 35pt

\lhead{\bigfont{\textcolor{phaseGold}{Phase}\textcolor{phaseGrey}{Capital LP}}}
\rhead{\textit{200 Clarendon Street $\cdot$ 25th Floor $\cdot$ Boston, MA 02116 \\
+1 617 587 5806 $\cdot$ inquiries@phasecap.com}}

\thispagestyle{fancy}
\twocolumn

\textbf{\textcolor{phaseGold}{KEY EXECUTIVES}} \\
  \textbf{John Donahue -} Chief Executive Officer \\
  \textbf{Geoff Goodell -} Chief Investment Officer \\
  \textbf{Pinaki Chatterjee -} Director of Research \\

\textbf{\textcolor{phaseGold}{BOARD OF MANAGERS}} \\
  \textbf{James Pallotta -} Raptor Group Holdings \\
  \textbf{Stuart Porter -} Denham Capital Management LP \\
  \textbf{Eric Pritchett -} Potamus Trading LLC \\
  \textbf{Robert Tishman -} Lightkeeper LLC \\
  \textbf{John Donahue -} PhaseCapital LP \\

\textbf{\textcolor{phaseGold}{FUND PROFILE}} \\
  \textbf{Type:} Systematic Macro \\
  \textbf{Minimum Investment:} \$2,000,000 \\
  \textbf{Redemption Terms:} Monthly, 15 day notice \\
  \textbf{Additions:} Monthly \\
  \textbf{Lock Up/Gate:} None \\

\textbf{\textcolor{phaseGold}{FEES}} (Founders Class) \\
  \textbf{Management Fee:} 1.25\% \\
  \textbf{Performance Fee:} None \\

\textbf{\textcolor{phaseGold}{INVESTMENT VEHICLES}} \\
  Phase II Fund LP \\
  Phase II Fund Ltd \\
  Separately Managed Accounts \\

\textbf{\textcolor{phaseGold}{SERVICE PROVIDERS}} \\
  \textbf{Prime Broker:} NewEdge USA, LLC \\
  \textbf{Auditor:} PriceWaterhouseCoopers \\
  \textbf{Administrator:}  SEI Global Services, Inc. \\
  \textbf{Legal Advisor:} Bingham McCutchen LLP \\
  \textbf{Cayman Legal Advisor:} Maples FS Limited \\
  \textbf{Custodian:} NewEdge USA, LLC \\
\vfill \eject

\textbf{\textcolor{phaseGold}{FIRM OVERVIEW}} \\
PhaseCapital LP (``PhaseCapital'') is a Boston-based registered investment
adviser that was founded in 2007 by a team of seasoned financial professionals
and academic researchers. The firm's heritage includes operating as a market maker
in the equity listed securities markets and the management of the requisite
risks at higher frequency timescales. The firm spun out its market-making effort
in 2011 and focused on developing a systematic macro strategy that was launched
in 2012. The core of the team has been together since the firm's inception. \\

\textbf{\textcolor{phaseGold}{FIRM INVESTMENT OBJECTIVE}} \\
PhaseCapital seeks to deliver attractive risk-adjusted returns through various
market environments by capturing a consistent level of volatility. 
PhaseCapital believes that forecasting is increasingly
problematic for all investment managers. Instead, PhaseCapital seeks
to measure risk and adjust our portfolio accordingly to outperform
static portfolios. \\

\textbf{\textcolor{phaseGold}{INVESTMENT UNIVERSE}} \\
  \textbf{Equities:} S\&P 500 and Russell 2000 e-mini futures contracts,
     State Street Sector SPDR ETFs \\
  \textbf{Credit:} iShares iBoxx corporate bond ETFs \\ 
  \textbf{Commodities:} Futures contracts representing energy, base metals and
    agricultural sectors \\ 
  \textbf{Interest Rates:} US Treasury futures representing 2, 5, 10, and 30 year
    maturities, plus the iShares TIPS ETF \\

\textbf{\textcolor{phaseGold}{CORE INVESTMENT STRATEGY}} \\
PhaseCapital employs an investment process that rejects forecasting and instead
emphasizes real-time measurement of risk and risk relationships within and
across asset classes. The strategy encompasses risk budgeting, intraday
rebalancing and enhanced diversification to provide the right risk at the
right time across a spectrum of risk premia. \\

PhaseCapital's flagship fund is most commonly compared to systematic macro
strategies. Some investors see it as an evolved version of risk parity, and
due to its solid performance in various macroeconomic environments, the fund is
often compared to absolute return approaches. The fund is also a candidate to
replace portions of static long-only equity and fixed income portfolios in
order to help investment programs respond more dynamically to changing
investment environments. \\

\newpage
\onecolumn

\textbf{\textcolor{phaseGold}{PORTFOLIO CONSTRUCTION}} \\
Portfolio construction begins by strategically budgeting risk
contributions across asset classes. The baseline allocation approximates a
traditional allocation of stocks (60\%), bonds (30\%) and commodities (10\%).
The risk contribution approach allows the portfolio to systematically adjust
the baseline allocation as diversification benefits between the asset classes
change over time. \\

Next, to deliver a more consistent volatility over time, the strategy
dynamically alters individual asset class exposures as risk and risk relationships
change within the portfolio. Using dense intraday data sets, PhaseCapital is
able to quickly reach statistically sound conclusions and tactically respond to
changing risk environments within and across asset classes. \\

Finally, within each asset class represented in the portfolio, the
strategy builds a ``smarter beta'' by employing some of the most liquid instruments
associated with sectors or subcategories to further harvest diversification. \\

\textbf{\textcolor{phaseGold}{MARKET OPPORTUNITY}} \\
PhaseCapital uses the tools and data collection capabilities of sophisticated
broker-dealers and traders to measure risk and execute trades. \\

By systematically rebalancing its portfolio throughout each trading day,
PhaseCapital offers its investors an edge over strategies that rely on static
portfolio targets, daily sampling methodologies and/or forecasting. \\

PhaseCapital dynamically captures broad sets of risk premia it believes will
appreciate over a market cycle. This dynamism allows PhaseCapital to reduce
or eliminate its exposure to certain risk premia during market dislocations
in order to protect it's portfolio. \\

\textbf{\textcolor{phaseGold}{RISKS TO CORE STRATEGY}} \\
Since PhaseCapital uses leverage and has broad exposures to various markets,
the strategy is exposed to ``gap risk'', or the risk that market drawdowns over
a short period of time will lead to drawdowns in the strategy. \\

Rallies accompanied by high volatility will likely cause PhaseCapital's strategy
to underperform simple balanced portfolios. \\

During periods of prolonged deflation with low volatility, the PhaseCapital
strategy may underperform due to its use of leverage and exposure to
dollar-denominated assets. \\

\textbf{\textcolor{phaseGold}{TEAM BIOGRAPHIES}} \\
  \textbf{Pinaki Chatterjee -} Director of Research, Portfolio Manager - Formerly
    at Bank of America/Merrill Lynch, Finlabs, Ph.D. Astronomy Harvard University,
    M.Sci Physics, University of Cambridge. \\
  \textbf{John Donahue -} Chief Executive Officer - Formerly at DeMatteo Monness,
    Compass Point Research, SG Cowen, B.S. Accountancy, Villanova \\
  \textbf{Brian Drew -} Director of Operations - Formerly at Harvard Management
    Company, B.S. Fairfield University \\
  \textbf{Chad FitzGerald -} Director of Business Development - Formerly at
    MatlinPatterson, SkyBridge Capital, GPS Partners, B.S. Political Science,
    Georgia Southern University \\
  \textbf{Geoff Goodell -} Chief Investment Officer - Formerly at Goldman Sachs
    \& Company, Ph.D. Computer Science, Harvard, S.B. Mathematics, Massachusetts
    Institute of Technology \\
  \textbf{Jackie Kelleher -} Investor Relations - Boston College \\
  \textbf{David Korsnack -} Director of Trading - Formerly at AT\&T, B.S. Business
    Administration, Boston University \\
  \textbf{Colin McSwiggen -} Investment Research Associate - Formerly at New
    England Complex Systems Institute, NJCTL, S.B. Mathematics S.B. Physics,
    Massachusetts Institute of Technology, M.A. Industrial Design Engineering,
    Royal College of Art, M.Sc. Industrial Design Engineering, Imperial College
    London \\
  \textbf{Lorena Timko -} Financial Controller and Chief Compliance Officer -
    Formerly at CYS Investments, Ernst \& Young, M.S. Accounting, B.B.A. University
    of Massachusetts Amherst, CPA \\

\newpage
\textbf{GENERAL DISCLAMERS} \\

This material is for informational purposes only and is being
furnished on a confidential basis to a limited number of prospective investors.
This presentation is not an offer to sell, nor a solicitation of an offer to
buy any security of any of the funds referenced in this material (each, a
``Fund'') or any other investment product.  Offers to sell or solicitations to
invest in any Fund are made only by means of a confidential offering memorandum
and in accordance with applicable securities laws.  Investors should review the
confidential offering memorandum (including, without limitation, the
information therein as to investment strategy, conflicts, and risks) prior to
making an investment decision.  Certain terms with respect to the Funds
referenced herein are subject to change. \\

This material has been prepared from original sources and data
believed to be reliable.  However no representations are made as to the
accuracy or completeness thereof.  No assurance can be given that the Funds
will invest in the manner described herein.  Certain information herein
reflects the opinion of PhaseCapital LP and is subject to change without
further notice.  An investment in a Fund involves a high degree of risk and is
suitable only for sophisticated investors. \\

For the purposes of United Kingdom legislation, this communication is
directed at, and may only be relied upon by, investment professionals, such
persons having professional experience in matters relating to investments and
who fall within Article 19 of The Financial Services and Markets Act 2000
(Financial Promotion) Order as amended 2001 (the ``Order'').  In addition, as
any collective investment scheme to which this communication may relate is not
categorized as a ``recognized collective investment scheme'' in the United
Kingdom, such collective investment scheme may not be, and is not being,
offered in the United Kingdom in circumstances that would contravene Section
238 of the Financial Services and Markets Act 2000. \\

\textbf{THIS MATERIAL MAY NOT BE REPRODUCED IN WHOLE OR IN PART, AND IT MAY
NOT BE DELIVERED TO ANY PERSON WITHOUT THE PRIOR WRITTEN CONSENT OF
PHASECAPITAL LP.}

\end{document}
