\documentclass[12pt]{article}

\usepackage[usenames]{color}
\usepackage[top=0.38in, bottom=0.38in, left=0.5in, right=0.5in]{geometry}
\usepackage{hyperref}
\definecolor{mygrey}{rgb}{0.85, 0.85, 0.85}
\pagestyle{empty}
\setlength{\tabcolsep}{0in}

\newcommand{\head}[1]{
  \colorbox{mygrey}{
    \begin{minipage}{7.35in}
      \center{\textbf{\large #1}}
    \end{minipage}
  }
}

\begin{document}
\footnotesize
\begin{tabular*}{7.3in}{@{\extracolsep{\fill}}lr}
  \hspace{-0.25in} \textbf{\LARGE David Michael Korsnack} & \href{mailto:dkorsnack@gmail.com}{\texttt{\large dkorsnack@gmail.com}} \\
  \hspace{-0.25in} {\large 32 Hillsdale $\cdot$ Irvine, CA $\cdot$ 92602} & \texttt{\large 617-230-3990}
\end{tabular*} \\
\head{Profile}
  \begin{list}{}{\leftmargin=0em}
    \item Entrepreneurial portfolio manager, trader, and financial technology
    professional with 12+ years of buy-side experience. Extensive knowledge
    of portfolio construction, risk management, algorithmic trading, and fund
    operations. Outstanding track record combined with professionalism, integrity,
    and the ability to work cohesively within a team. 
  \end{list}
\head{Professional Experience} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{\large Tee Hub LLC} $\vert$ Large Single Family Office $\vert$ Irvine, CA & \textbf{February 2018 -- Current} \\
    \hline
  \end{tabular*} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{Portfolio Manager - Capital Preservation, Risk Managed Growth}
  \end{tabular*}
    \begin{list}{\labelitemiv}{\leftmargin=0em}
      \item \textit{Portfolio \& Risk Management}: Developed systematic investment
        process for liquid, electronic exchange traded Derivatives (Futures \& Options)
        utilizing AI techniques to manage risk and exploit real-time changes
        in asset-class volatility.
      \item \textit{Research}: Custom built backtesting infrastructure to test and
        and improve proprietary trading strategies.
      \item \textit{Trading \& Operations}: Automated firm-wide trading via
        systematic execution algorithms with ``point-and-click" functionality
        leveraging Bloomberg EMSX \& API, reducing trading slippage 20\%. 
      \item \textit{Data Services}: Migrated from on-site data center to ``the
        cloud" with zero downtime, resulting in direct operational
        impact on performance. Enhanced data retrieval methods to increase
        efficiency, boosting speed 2-5x over previous capabilities.
  \end{list}
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{\large PhaseCapital LP} $\vert$ SEC Registered Investment Advisor $\vert$ Boston, MA & \textbf{March 2008 -- November 2017} \\
    \hline
  \end{tabular*} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{Partner - Portfolio Manager, Trading \& Technology} & \textbf{January 2012 -- November 2017}
  \end{tabular*}
    \begin{list}{\labelitemiv}{\leftmargin=0em}
      \item \textit{Business Development}: Pitched institutional investors
        in over 500+ global meetings over a three year period, increasing AUM from
        \$20M in partner capital to nearly \$500M in Sovereign Wealth, Private/Public Pension, and
        Family Office investments.
      \item \textit{Portfolio \& Risk Management}: Continuously rebalanced
        investor specific, multi-asset portfolios (including Equity, Fixed Income,
        \& Alternatives). Implemented dynamic hedging policy using liquid Futures \& Options.
      \item \textit{Research}: Investigated ``tactical risk budgeting" opportunities
        by analyzing fundamentals of the portfolio's risk profile. Studied real-time
        covariance estimation across disparate markets to expand investment universe. 
      \item \textit{Trading \& Operations}: Optimized execution algorithms,
       expanded execution desk to include global securities, and implemented
       multi-strategy allocation procedures to achieve best execution. Worked
       closely with multiple brokers and custodians to automate pre- and
       post-trade operations via several APIs and connectivity methods. 
      \item \textit{Data Services}: Redesigned data acquisition/storage to
        minimize costs while expanding into new markets and asset classes.
    \end{list}
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{Associate - Trading \& Technology} $\vert$ Creation of \textbf{Potamus Trading LLC} & \textbf{March 2008 -- December 2011}
  \end{tabular*}
    \begin{list}{\labelitemiv}{\leftmargin=0em}
      \item \textit{Portfolio \& Risk Management}: Created Process Dependency Tree and
        Real-Time P\&L Monitor.
      \item \textit{Trading \& Operations}: Designed, built, and maintained
        algorithmic trading technology including the OMS, EMS, SOR, CEP, and FIX engine.
        Assisted back-office team and several business partners to reconcile
        trades and attribute profits/losses.
      \item \textit{Data Services}: Managed dense data sets from multiple vendors
        for firm-wide usage via causal, relational databases.
    \end{list}
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{\large AT\&T} $\vert$ Corporate Finance \& Strategy $\vert$ Bedminster, NJ & \textbf{August 2005 -- February 2008} \\
    \hline
  \end{tabular*} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{Financial Leadership Program}
  \end{tabular*}
  \begin{list}{}{\leftmargin=0em}
    \item Three rotations in high profile, decision making positions in a
      broad selection of AT\&T's Finance Organization
  \end{list}
\head{Education \& Certification} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{\large Boston University} $\vert$ BS in Business Administration $\vert$ Boston, MA & \textbf{September 2001 -- May 2005} \\
    \hline
    \textbf{Probability \& Statistics Head Teaching Assistant}, Questrom School of Business & \textbf{June 2002 -- June 2004}
  \end{tabular*}
  \begin{list}{\labelitemiv}{\leftmargin=0em}
    \item \textbf{FRM} (Financial Risk Manager) Certified; active member of
      \textbf{GARP} (Global Association of Risk Professionals)
   \item \textbf{CFA} (Chartered Financial Analyst) Level II Candidate \hfill
     $\cdot$ \textbf{Series 3} (National Commodity Futures) Licensed
  \end{list}
\head{Technical Skills}
  \begin{list}{\labelitemiv}{\leftmargin=0em}
    \item \textit{Programming}: Python, SQL (My, Postgre, MS), Git, SVN, Java,
      Scala, R, Shell Scripting, Visual Basic, \LaTeX
    %\item \textit{Operating Systems}: Debian \& Red Hat Linux, Windows, Macintosh, Ubuntu
    \item \textit{Software}: Bloomberg (Terminal, AIM, EMSX, BPIPE \& SAPI),
      Microsoft Office, FactSet, Geneva, Charles River 
  \end{list}
\head{Personal}
  \begin{list}{\labelitemiv}{\leftmargin=0em}
    \item \textit{Strengths}: Positive attitude, problem solving, short debug cycles,
      teamwork, communication, meticulousness, tenacity
    \item \textit{Interests}: Family, games of strategy/chance, traveling, golf,
      fly-fishing, hiking, snowboarding, reading
  \end{list}
\end{document}
