\documentclass[12pt]{article}

\usepackage[usenames]{color}
\usepackage[top=0.38in, bottom=0.38in, left=0.5in, right=0.5in]{geometry}
\usepackage{hyperref}
\definecolor{mygrey}{rgb}{0.85, 0.85, 0.85}
\pagestyle{empty}
\setlength{\tabcolsep}{0in}

\newcommand{\head}[1]{
  \colorbox{mygrey}{
    \begin{minipage}{7.35in}
      \center{\textbf{\large #1}}
    \end{minipage}
  }
}

\begin{document}
\footnotesize
\begin{tabular*}{7.3in}{@{\extracolsep{\fill}}lr}
  \hspace{-0.25in} \textbf{\LARGE David Michael Korsnack} & \href{mailto:dkorsnack@gmail.com}{\texttt{\large dkorsnack@gmail.com}} \\
  \hspace{-0.25in} {\large 32 Hillsdale $\cdot$ Irvine, CA $\cdot$ 92602} & \texttt{\large 617-230-3990}
\end{tabular*} \\
\head{Objective}
  \begin{list}{}{\leftmargin=0em}
    \item Seeking position as quantitative developer focused on portfolio
      risk management at leading global investment firm.
  \end{list}
\head{Profile}
  \begin{list}{}{\leftmargin=0em}
    \item Accomplished ``fin-tech" professional with 10 years of buy-side
    experience managing risk-based portfolios. Extensive knowledge of portfolio construction,
    risk management, quantitative research, algorithmic trading, and fund operations.
    Outstanding performance track record combined with professionalism, integrity,
    and the ability to work cohesively within a team. 
  \end{list}
\head{Professional Experience} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{\large PhaseCapital LP}, Boston, MA & \textbf{March 2008 -- October 2017} \\
    \hline
  \end{tabular*} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{Director - Portfolio Management \& Risk} & \textbf{January 2012 -- October 2017}
  \end{tabular*}
    \begin{list}{\labelitemiv}{\leftmargin=1em}
      \item \textit{Portfolio Management \& Risk}: Optimized and continuously rebalanced
        investor specific, multi-asset portfolios (including Equity, Fixed Income,
        \& Alternatives). Implemented dynamic hedging policy using liquid Futures \& Options.
      \item \textit{Research}: Analyzed ``tactical risk budgeting" opportunities
        by investigating fundamentals of the portfolio's risk profile. Studied real-time
        covariance estimation across disparate markets and economic scenarios to
        expand investment universe. 
      \item \textit{Trading}: Optimized execution algorithms and reduced trade
        frictions with negligible impact on risk-adjusted return. Expanded execution
        desk to include global securities and multi-strategy allocation procedures
        to achieve best execution.
      \item \textit{Data Services}: Rearchitected data acquisition/storage to
        minimize costs while expanding into new markets and asset classes. Migrated
        from physical data center to cloud-based framework with zero downtime,
        resulting in direct operational impact on performance. Enhanced data
        retrieval methods to increase efficiency, boosting speed 2-5x over
        previous capabilities.
      \item \textit{Operations}: Worked closely with data providers and clearing
        brokers to automate pre- and post-trade operations. Improved infrastructure
        to trade over multiple prime and execution brokers via several APIs and
        connectivity methods. 
    \end{list}
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{Associate - Trading \& Technology} & \textbf{March 2008 -- December 2011}
  \end{tabular*}
    \begin{list}{\labelitemiv}{\leftmargin=1em}
      \item \textit{Trading}: Designed, built, and maintained proprietary algorithmic
        trading technology including the Execution Management System, Smart Order
        Router, Complex Event Processor, and Financial Information Exchange Engine.
      \item \textit{Data Services}: Managed dense data sets from multiple vendors
        for firm-wide usage via causal, relational databases.
      \item \textit{Portfolio Management}: Created Process Dependency Tree and
        Real-Time P\&L Monitor.
      \item \textit{Research}: Applied information theoretic techniques to real-time
        market data leveraging stress-testing and Monte Carlo simulation to recognize
        profitable trading opportunities and bet-size them for maximum return per unit
        of risk.
      \item \textit{Operations}: Worked closely with back-office and several
        business partners to reconcile trades and attribute profits/losses.
    \end{list}
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{\large AT\&T}, Bedminster, NJ & \textbf{August 2005 -- March 2008} \\
    \hline
  \end{tabular*} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{Financial Leadership Program}
  \end{tabular*}
  \begin{list}{}{\leftmargin=0em}
    \item Three rotations in high profile, decision making positions in a
      broad selection of AT\&T's Finance Organization
  \end{list}
\head{Education \& Certification} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{\large Boston University}, Boston, MA; BS in Business Administration & \textbf{September 2001 -- May 2005} \\
    \hline
    \textbf{Probability \& Statistics Head Teaching Assistant}, Questrom School of Business & \textbf{June 2002 -- June 2004}
  \end{tabular*}
  \begin{list}{\labelitemiv}{\leftmargin=1em}
    \item \textbf{FRM} (Financial Risk Manager) Certified and member of
      \textbf{GARP} (Global Association of Risk Professionals)
   \item \textbf{Series 3} Licensed
    \item \textbf{CFA} (Chartered Financial Analyst) Candidate, Level II
  \end{list}
\head{Technical Skills}
  \begin{list}{\labelitemiv}{\leftmargin=1em}
    \item \textit{Programming}: Python, SQL, Shell Scripting, Java, R, Scala, Visual Basic, \LaTeX
    \item \textit{Operating Systems}: Debian \& Red Hat Linux, Windows, Macintosh, Ubuntu
    \item \textit{Software}: Bloomberg (Terminal, AIM, TradeBook, EMSX, BPIPE \& SAPI),
      Microsoft Office, SVN, Git, MatLab
  \end{list}
\head{Personal}
  \begin{list}{\labelitemiv}{\leftmargin=1em}
    \item \textit{Strengths}: Positive attitude, problem solving, short debug cycles,
      teamwork, communication, meticulousness, tenacity
    \item \textit{Interests}: (in no particular order) family, games of strategy/chance,
      traveling, golf, fly-fishing, hiking, reading
    \item \textit{References}: Available upon request
  \end{list}
\end{document}
