\documentclass[12pt]{article}

\usepackage[usenames]{color}
\usepackage[top=0.38in, bottom=0.38in, left=0.5in, right=0.5in]{geometry}
\usepackage{hyperref}
\definecolor{mygrey}{rgb}{0.85, 0.85, 0.85}
\pagestyle{empty}
\setlength{\tabcolsep}{0in}

\newcommand{\head}[1]{
  \colorbox{mygrey}{
    \begin{minipage}{7.35in}
      \center{\textbf{\large #1}}
    \end{minipage}
  }
}

\begin{document}
\footnotesize
\begin{tabular*}{7.3in}{@{\extracolsep{\fill}}lr}
  \hspace{-0.25in} \textbf{\LARGE David Michael Korsnack} & \href{mailto:dkorsnack@gmail.com}{\texttt{\large dkorsnack@gmail.com}} \\
  \hspace{-0.25in} {\large 32 Hillsdale $\cdot$ Irvine, CA $\cdot$ 92602} & \texttt{\large 617-230-3990}
\end{tabular*} \\
\head{Objective}
  \begin{list}{}{\leftmargin=0em}
    \item Seeking position in quantitative finance / risk management at global
      institutional investment firm.
  \end{list}
\head{Profile}
  \begin{list}{}{\leftmargin=0em}
    \item Financial technology professional \& quantitative software
    developer with 10 years of buy-side experience. Extensive knowledge of portfolio
    construction, risk management, quantitative research, algorithmic trading, and
    fund operations. Outstanding performance track record combined with professionalism,
    integrity, and the ability to work cohesively within a team. 
  \end{list}
\head{Professional Experience} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{\large PhaseCapital LP}, Boston, MA & \textbf{March 2008 -- October 2017} \\
    \hline
  \end{tabular*} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{Director - Trading \& Technology} & \textbf{January 2012 -- October 2017}
  \end{tabular*}
    \begin{list}{\labelitemiv}{\leftmargin=1em}
      \item \textit{Research}: Improved ``risk budgeting" portfolio
        optimizations by implementing real-time covariance estimation across
        disparate markets and economic scenarios, increasing risk-adjusted returns
        and expanding the investment universe. 
      \item \textit{Portfolio Management}: Built factor models guiding
        multi-asset portfolio investment decisions including global Equity, Fixed
        Income, \& Alternative securities. Implemented dynamic hedging policy
        using liquid Futures \& Options.
      \item \textit{Data Services}: Rearchitected data acquisition/storage 
        from physical data center to cloud-based framework with zero downtime,
        resulting in direct operational impact on performance. Enhanced data
        retrieval methods to increase efficiency, boosting speed 2-5x over
        previous capabilities.
      \item \textit{Trading}: Improved execution algorithms via transaction
        cost analysis increasing overall portfolio risk adjusted returns. Expanded
        execution desk to include global securities and multi-strategy allocation
        procedures to achieve best execution.
      \item \textit{Operations}: Worked closely with data providers and clearing
        brokers to automate pre- and post-trade operations. Improved infrastructure
        to trade over multiple prime and execution brokers via several APIs and
        connectivity methods. 
    \end{list}
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{Associate - Trading \& Technology} & \textbf{March 2008 -- December 2011}
  \end{tabular*}
    \begin{list}{\labelitemiv}{\leftmargin=1em}
      \item \textit{Research}: Applied information theoretic techniques on historic
        / real-time market data to recognize profitable trading opportunities
        and bet-size them for maximum return per unit of risk.
      \item \textit{Portfolio Management}: Created, managed, \& maintained Process
        Dependency Software and Real-Time P\&L Monitor.
      \item \textit{Data Services}: Managed dense data sets from multiple vendors
        for firm-wide usage via causal, relational databases.
      \item \textit{Trading}: Designed, built, and maintained proprietary algorithmic
        trading technology including the Execution Management System, Smart Order
        Router, Complex Event Processor, and Financial Information Exchange Engine.
      \item \textit{Operations}: Assisted back-office team and business
        partners to automate trade reconciliation and profit/loss attribution.
    \end{list}
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{\large AT\&T}, Bedminster, NJ & \textbf{August 2005 -- March 2008} \\
    \hline
  \end{tabular*} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{Financial Leadership Program}
  \end{tabular*}
  \begin{list}{}{\leftmargin=0em}
    \item Three rotations in high profile, decision making positions in a
      broad selection of AT\&T's Finance Organization
  \end{list}
\head{Education \& Certification} \\
  \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
    \textbf{\large Boston University}, Boston, MA; BS in Business Administration & \textbf{September 2001 -- May 2005} \\
    \hline
    \textbf{Probability \& Statistics Head Teaching Assistant}, Questrom School of Business & \textbf{June 2002 -- June 2004}
  \end{tabular*}
  \begin{list}{\labelitemiv}{\leftmargin=1em}
    \item \textbf{FRM} (Financial Risk Manager) Certified and member of
      \textbf{GARP} (Global Association of Risk Professionals)
   \item \textbf{Series 3} Licensed
    \item \textbf{CFA} (Chartered Financial Analyst) Candidate, Level II
  \end{list}
\head{Technical Skills}
  \begin{list}{\labelitemiv}{\leftmargin=1em}
    \item \textit{Programming}: Python, SQL (My, Postgre, \& MS), Java, Scala, R, Shell Scripting, Visual Basic, \LaTeX
    \item \textit{Operating Systems}: Debian \& Red Hat Linux, Windows, Macintosh, Ubuntu
    \item \textit{Software}: Bloomberg (Terminal, AIM, TradeBook, EMSX, BPIPE, \& SAPI),
      Microsoft Office, SVN, Git, MatLab
  \end{list}
\head{Personal}
  \begin{list}{\labelitemiv}{\leftmargin=1em}
    \item \textit{Strengths}: Positive attitude, problem solving, short debug cycles,
      teamwork, communication, meticulousness, tenacity
    \item \textit{Interests}: (in no particular order) family, games of strategy/chance,
      traveling, golf, fly-fishing, hiking, reading
    \item \textit{References}: Available upon request
  \end{list}
\end{document}
